Racial and Ethnic Differences in ETI

### 2023-09-20 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
moving race and ETI to lambda

```{r}
#| eval: false
t = annual %>% select(eDWID,ReviewYear,mean_ppFEV) %>% na.omit(.)
model = list(mean_ppFEV ~ 0 + ReviewYear, 
              ~ 0 + ReviewYear)
fit = mcp(model,data = t,cores=4,chains = 4)
plot(fit)
```

>>>>

```{r}
#| cache: true
t = annual %>% select(eDWID,ReviewYear,mean_ppFEV) %>% na.omit(.)
model = list(mean_ppFEV ~ 0 + ReviewYear, 
              ~ 0 + ReviewYear)
fit = mcp(model,data = t,cores=4,chains = 4)
plot(fit)
```
